An analysis of interrelations between economic and environmental variables in Australian Winegrowing.

### 2023-10-03 article.tex
Mardi edits

% FIXME: Stop writing chronologically. Write by significance.

@@

In the past decade, the Australian winegrowing industry has undergone a variety of pressures, such as changing market demands, disease and drought \citep{wineaustraliaAustralianWineProduction2021}. Furthermore, natural resources are likely to decrease, as pressures from climate change increase, making it more important than ever to improve the efficiency and sustainability of crops \citep{agdeeNationalGreenhouseAccounts2021}. It has become crucial for those in the wine industry to address issues relating to environmental sustainability and economic viability, with a growing need for the industry to close the research gaps between sustainable practices and their real and perceived environmental and economic advantages \citep{montalvo-falconSustainabilityResearchWine2023,ouvrardDoesSustainabilityPush2020}. This paper aims to provide a comprehensive analysis of the intricate relationships between economic and environmental variables within the winegrowing sector. By employing statistical machine learning we show how interconnected vineyard variables are. Utilising a ten year data set that spans Australia we show the predominant 
elements in classifying region and year, % FIXME: A reader will ask: why would i want to predict region and year?
 as well as determining a vineyards potential operational costs and profit.
\par
This analysis utilises 
XGBoosted trees % FIXME: Why XGBoosted trees?
 to classify region and year; and to determine operating cost and profit of Australian vineyards. Classification and regression trees are 
 utilised as surrogate models %FIXME: Why are we utilising surrogate models?
to shed insight into the key partitions used by the XGBoost ensembles. Variable importance is further used to illustrate the 
interconnectedness % FIXME: What kind of interconnectedness?
of the different predictor variables, and to show the similarity in
variable importance % FIXME: What does variable importance mean in this context?
between different response variables (particularly between region and operational cost). This study aims to assist in uncovering 
the complexity of variables %FIXME: This is too vague, what makes them complex? why are the complex? etc
that are affected by a variety of vineyard management decisions to illustrate 
complex interplay of variables. % FIXME: What do you mean by complex interplay? Like what? An example?
This study endeavours to gain insight into the 
similarity % FIXME: Why do we want to know the similarity?
 in predictor variable importance between year, region, operational costs and profit.

@@

% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia. Australia's national wine industry sustainability program, which aims to facilitate grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by the SWA is entered manually by winegrowers using a web based interface tool. A total of 6091 observations were collected from 2012/2013 to 2021/2022 financial years. 23 variables were used for each observation reflecting a vineyards account for the given year (see Table \ref{tab:vars}). 
The profit variable was transformed % FIXME: What was it before?
and included as another separate variable, profitable; depicting whether a vineyard was profitable or not.
\par

\begin{table}[] 
 \label{tab:vars}
 \caption{Summary of variables used in the analysis. The recorded column indicate values that were either greater than zero or that were not missing.}\label{tab:summary}
 \begin{tabular}{@{}ccccl@{}}
  \toprule
  \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{\begin{tabular}[c]{@{}c@{}}Number of\\ Classes\end{tabular}} & \\ \midrule
  Water Used & Mega Litres & 5846 & & \\
  Diesel & Litres & 5585 & & \\
  Biodiesel & Litres & 25 & & \\
  LPG & Litres & 958 & & \\
  Herbicide Spray & Times per year & 2026 & & \\
  Year & Class & 6091 & 10 & \\
  Disease & Class & 6091 & 2 & \\
  Region & Class & 6091 & 58 & \\
  Solar & Kilowatt Hours & 622 & & \\
  Irrigation Type & Class & 6091 & 20 & \\
  Petrol & Litres & 4309 & & \\
  Slashing & Times per year & 2290 & & \\
  Yield & Tonnes & 5935 & & \\
  Irrigation Energy & Class & 6091 & 16 & \\
  Area Harvested & Hectares & 6091 & & \\
  Electricity & Kilowatt Hours & 1015 & & \\
  Insecticide Spray & Times per year & 1092 & & \\
  Fertiliser & \begin{tabular}[c]{@{}c@{}}Kilograms \\ of Nitrogen\end{tabular} & 795 & & \\
  Fungicide Spray & Times per year & 2260 & & \\
  Cover Crop & Class & 6091 & 32 & \\
  Water Type & Class & 6091 & 39 & \\
  Profit & AUD & 853 & & \\
  Operating Costs & AUD & 853 & & \\ \bottomrule
  \end{tabular}
\end{table}

@@

There was a pronounced difference in accuracy between the regression tree and the XGBoost model when predicting Operating costs. With the regression tree achieving an $R^2$ of 0.0931 (with a standard deviation of 0.0197) in its cross validation. The XGBoosted regression ensemble achieved an $R^2$ of 0.8025 (with a standard deviation of 0.1033).
\par
Within the XGBoost ensemble's nodes for operating costs (see figure \ref{fig:operating_costs_sankey}) fuel, water, area and yield occurred the most, similarly to region. Both diesel and petrol were of more relative importance (being ranked higher) in operating costs than water was compared with region. It is surprising that electricity, slashing and spraying was not more prominent in operating costs. 
% FIXME: Me and Kate talked about this. The diagrams, their context and justification go into the methods. How to interpret them needs to be better outlined here. You need to affirm peoples intition of them and the significance of more ribbons going out than in as well as why we are only using 10 variables.
However, Figure \ref{fig:year_sankey} shows that electricity, slashing and spraying are important variables in determining area and yield.

Electricity in particular is used predominantly for irrigation and so is related largely to the size of a vineyard. However, slashing and spraying are measured in discrete tractor passes and show a surprising connection to the overall size of a vineyard, despite not being scaled to any measure of size. This would mean that, although measured as the same increment, a slashing or spraying pass in a larger vineyard would consume more fuel and wages than in a smaller vineyard.

@@

\begin{figure}
 \resizebox{\textwidth}{!}{
 \includegraphics{profit.pdf}}
 \caption{Decision tree predicting Profit. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:profit_tree}
\end{figure}

@@

% FIXME: Moved here from results. Find a place for this lost puppy!
% It is reasonable that regions, being subjected to different rainfalls and temperatures, would require different amounts of water, and would have access to different water sources. The relation of area harvested and fuel (particularly petrol) is prominent with other predictors. Due to the wide variety of uses of petrol and diesel, it is likely that they are representative of other activities within the vineyard, such as pruning and harvesting. With predictors such as yield and area being highly interconnected as they likely operate as proxy variables to other factors, possibly other present variables.

Several physical parameters such as climate, geology and soil are predetermined by a vineyard's location; making it a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. 
The association between yield and region is demonstrated by its position as fourth most occurring variable within the nodes of the XGBoosted ensemble which determined region (see Figure \ref{fig:region_sankey}). % FIXME: Clunky phrasing

The association with area and region is likely a connection to the change in land costs, with inland Australian areas (particularly of lower rainfall) being substantially cheaper to buy than coastal regions, allowing larger areas to be purchased \citep{willchancellorMeasuringAustralianBroadacre2019}.

@@

Regions with lower land costs are also warmer \citep{willchancellorMeasuringAustralianBroadacre2019}, which is known to be beneficial in hastening the ripening process of winegrapes \citep{webbObservedTrendsWinegrape2011}. Warmer regions are also associated with lower quality grapes, caused largely due to this hastened ripening \citep{botting1996canopy}. In general warmer regions have been associated with lower yields due to their generally lower rainfall, which can be mitigated through applying excess water \citep{campsGrapeHarvestYield2012}. It is likely that the combination of larger vineyards with higher water use is a determining factor in classifying regions which favour larger production of lower quality grapes; reflected through the variables' importance of water use in the XGBoost ensemble. The practice of utilising larger quantities of water for inland Australian wine crops is partly reflected in the prior use of flood style irrigation to saturate soil \citep{bgcoombeGrapeBerryDevelopment2004}. This classification can be contrasted with other warmer regions of higher rainfall that use the warmer climate to concentrate their grapes, increasing the flavour profile (and thus quality) \citep{goodwinijeriepRegulatedDeficitIrrigation1992,mgmccarthyEffectCropLoad1986}. This is possibly the connection between the presence of the Hunter Valley within the XGBoost ensemble that determined profit (see Figure \ref{fig:profit_sankey}). With this connection reflecting the restriction of possible strategies employable by winegrowers between different regions.

@@

In part some winegrowing strategies are restricted simply through access to water resources, being reflected through the region classification tree (see Figure \ref{fig:region_tree}). Regions are likely to have varying access to different water sources, such as those along the River Murray being able to utilise river water for crops unlike most coastal regions. Similarly, the connection between region and fuel use is likely an indicator of the level of infrastructure within the region. Where, the need to pressurise irrigation systems from river water or to generate power would require larger amounts of diesel and petrol.

@@

Operational costs showed similar importance across fuel, water and tractor use. The dominating factor of area likely played a large part in determining how costly a tractor pass would be, or in defining the ratio of water applied to the amount of vines. The node frequency was high for area but much lower in general across the other variables, which could indicate the need to be more circumstantial in determining operational costs. Although it was attempted to capture the complexity between how variables interacted when determining operational costs (see Figure \ref{fig:operating_costs_sankey}), it is likely yet more complicated still. An example of how interrelated operational costs can be, is the optimisation of tractor passes being shown to reduce energy use in vineyards, decreasing running costs, as well as reducing soil compaction \citep{capelloEffectsTractorPasses2019}. 

@@

Decisions made on the ground have far-reaching effects and are difficult to completely capture. Greater tractor use as a preventative measure for occurrences such as disease, may incur higher operational costs but could be critical in preventing long term losses. With factors such as erosion and soil health being difficult to capture but also influenced by tractor use \citep{capelloEffectsTractorPasses2019,capelloPermanentCoverSoil2020}. Although, performing well in $R^2$, the ability to predict operational costs is limited by the variables incorporated. Reductions in fuel, water and tractor use are obvious methods to reduce operational costs but not necessarily achievable decisions. Without fully capturing more granular activities such as the specifics of what fuel was used for, it is hard to determine what decisions specifically influence the operational costs.

@@

Although less important in the XGBoost ensembles for profit, the variables: cover crops, fungicide spraying and slashing are likely linked to broad environmental properties of regions (see Figure \ref{fig:region_sankey} and \ref{fig:profit_sankey}). Rainfall being related to fungal growth and disease, as well as weeds. With cover crops being an effective and sustainable method to alleviate these issues \citep{delpuechAdaptingCoverCrop2018}. It is difficult to extrapolate findings to these methods and the reason for their use due to the broad and varying definition of the regions. Utilising the Geographical Indicator regions defined by Wine Australia \citep{wineaustraliaWineAustraliaOpenData2021} is a limitation, as it is too broad to fully capture a vineyards location and its influence on more granular variables. The reasoning for using approaches such as cover crops can be widely varying. Where, a cover crop may be employed to help increase soil water retention, reduce erosion, increase biodiversity and reduce weeds \citep{capelloEffectsTractorPasses2019,capelloPermanentCoverSoil2020,delpuechAdaptingCoverCrop2018}. However, cover crops can introduce competition with grapevines and may reduce yield depending upon the plants used and the density of the cover crop \citep{goslingLongtermChangesSoil2005,monteiroInfluenceCoverCrop2007}. A more granular definition of region may help to better discern the differences in practices, and the reason for employing them. More sophisticated models, specifically those that utilise expert opinion, may also help to capture and address the decision making process. An example is the optimisation of fungicide sprays using Bayesian models that forecast disease risk \citep{luDiseaseRiskForecasting2020}.

@@

This study has provided valuable insights into the multifaceted dynamics governing operational costs, different yearly effects and vineyard regions. Highlighting the complex interrelatedness of variables within a vineyard. The paper underscores how factors such as water and fuel use intersect to impact operational costs. How different yearly events affect these operations and the significance of context-specific decision-making. While this investigation utilised a broad regional classification, the potential benefits of adopting a more nuanced approach and incorporating expert knowledge have been highlighted. By delving deeper into the complex interplay of variables, further advancements can be made in optimising vineyard management strategies for lowering operational costs and enhancing sustainability.

@@

 The classification tree and XGBoosted ensemble performed similarly for classifying year with 35.20\% (6.28\% standard deviation) and 51.81\% (42.20\% validation accuracy) respectively. Electricity and the type of irrigation were highly influential within the classification tree. Similarly, electricity was the most frequently occurring node in the XGBoost ensemble. Other variables such as slashing passes, and fungicide and herbicide spraying were more prevalent than in the classification tree. Weed and disease outbreaks are likely an influential factor when classifying different years, making the decisions to spray and slash unique factors that differ year to year. Climatic differences between years are likely tied to the influence of yield and water use.
 \par
 Over half of the interrelated importance of the predictor variables is dominated by area harvested, yield and slashing passes. Although all the predictor variables are highly connected, their relative importance is not as prominent as the three major variables. It is of particular note of the relative importance of slashing to area, fuel and yield; as these are not directly related activities. The connection between slashing and spraying is that those who do a set number of spraying or slashing passes tended to do that many passes for all slashing and spraying activities.

>>>>

% FIXME: Stop writing chronologically. Write by significance.
% TODO: Should the models be redone as a factor of area? instead of including area? The ensemble should effectively pick this up I do not think it needs to be done.

@@

In the past decade, the Australian grape and wine industry has undergone a variety of pressures, including changing market demands, disease and drought \citep{wineaustraliaAustralianWineProduction2021}. Furthermore, natural resources are likely to decrease, as pressures from climate change increase, making it more important than ever to improve the efficiency and sustainability of crops \citep{agdeeNationalGreenhouseAccounts2021}. It has become crucial for those in the wine industry to address issues relating to environmental sustainability and economic viability, with a growing need for the industry to close the research gaps between sustainable practices and their real and perceived environmental and economic advantages \citep{montalvo-falconSustainabilityResearchWine2023,ouvrardDoesSustainabilityPush2020}. This paper aims to provide a comprehensive analysis of the intricate relationships between economic and environmental variables within the winegrowing sector. By employing statistical machine learning we show how interconnected vineyard variables are. Utilising a ten year data set that spans Australia we show the predominant 
elements in classifying region and year, % FIXME: A reader will ask: why would i want to predict region and year?
 as well as determining a vineyards potential operational costs and profit.
\par
This analysis utilises 
XGBoosted trees % FIXME: Why XGBoosted trees?
 to classify region and year; and to determine operating cost and profit of Australian vineyards. Classification and regression trees are 
 utilised as surrogate models %FIXME: Why are we utilising surrogate models?
to shed insight into the key partitions used by the XGBoost ensembles. Variable importance is further used to illustrate the 
interconnectedness % FIXME: What kind of interconnectedness?
of the different predictor variables, and to show the similarity in
variable importance % FIXME: What does variable importance mean in this context?
between different response variables (particularly between region and operational cost). This study aims to assist in uncovering 
the complexity of variables %FIXME: This is too vague, what makes them complex? why are the complex? etc
that are affected by a variety of vineyard management decisions to illustrate 
complex interplay of variables. % FIXME: What do you mean by complex interplay? Like what? An example?
This study endeavours to gain insight into the 
similarity % FIXME: Why do we want to know the similarity?
 in predictor variable importance between year, region, operational costs and profit.

@@

% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia. Australia's national wine industry sustainability program. The program aims to facilitate grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by the SWA is entered manually by winegrowers using a web based interface tool. A total of 6091 observations were collected from 2012/2013 to 2021/2022 financial years. 23 variables were used for each observation reflecting a vineyards account for the given year (see Table \ref{tab:vars}). 
The profit variable was transformed % FIXME: What was it before?
and included as another separate variable, profitable; depicting whether a vineyard was profitable or not.
\par

\begin{table}[] 
 \label{tab:vars}
 \caption{Summary of variables used in the analysis. The recorded column indicate the number of values that were either greater than zero or that were not missing.}\label{tab:summary}
 \begin{tabular}{@{}ccccl@{}}
  \toprule
  \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{\begin{tabular}[c]{@{}c@{}}Number of\\ Classes\end{tabular}} & \\ \midrule
  Water Used & Mega Litres & 5846 & & \\
  Diesel & Litres & 5585 & & \\
  Biodiesel & Litres & 25 & & \\
  LPG & Litres & 958 & & \\
  Herbicide Spray & Times per year & 2026 & & \\
  Year & Class & 6091 & 10 & \\
  Disease & Class & 6091 & 2 & \\
  Region & Class & 6091 & 58 & \\
  Solar & Kilowatt Hours & 622 & & \\
  Irrigation Type & Class & 6091 & 20 & \\
  Petrol & Litres & 4309 & & \\
  Slashing & Times per year & 2290 & & \\
  Yield & Tonnes & 5935 & & \\
  Irrigation Energy & Class & 6091 & 16 & \\
  Area Harvested & Hectares & 6091 & & \\
  Electricity & Kilowatt Hours & 1015 & & \\
  Insecticide Spray & Times per year & 1092 & & \\
  Fertiliser & \begin{tabular}[c]{@{}c@{}}Kilograms \\ of Nitrogen\end{tabular} & 795 & & \\
  Fungicide Spray & Times per year & 2260 & & \\
  Cover Crop & Class & 6091 & 32 & \\
  Water Type & Class & 6091 & 39 & \\
  Profit & AUD & 853 & & \\
  Operating Costs & AUD & 853 & & \\ \bottomrule
  \end{tabular}
\end{table}

@@

There was a pronounced difference in accuracy between the regression tree and the XGBoost model when predicting Operating costs. With the regression tree achieving an $R^2$ of 0.0931 (with a standard deviation of 0.0197) in its cross validation. The XGBoosted regression ensemble achieved an $R^2$ of 0.8025 (with a standard deviation of 0.1033).
\par
Within the XGBoost ensemble's nodes for operating costs (see figure \ref{fig:operating_costs_sankey}) fuel, water, area and yield occurred the most, similarly to region. Both diesel and petrol were of more relative importance (being ranked higher) in operating costs than water was compared with region. It is surprising that electricity, slashing and spraying passes was not more prominent in operating costs. 
% FIXME: Me and Kate talked about this. The diagrams, their context and justification go into the methods. How to interpret them needs to be better outlined here. You need to affirm peoples intition of them and the significance of more ribbons going out than in as well as why we are only using 10 variables.
However, Figure \ref{fig:year_sankey} shows that electricity, slashing and spraying are important variables in determining area and yield.

Electricity in particular is used predominantly for irrigation and so is related largely to the size of a vineyard. However, slashing and spraying are measured in discrete tractor passes and show a surprising connection to the overall size of a vineyard, despite not being scaled to any measure of size. This would mean that, although measured as the same increment, a slashing or spraying pass in a larger vineyard would consume more fuel and wages than in a smaller vineyard. % FIXME: May need to maintain bigger vineyards are more likely to have more staff verse small owner operators. Those extra staff may be trying to keep employers busy be sending them slashing (this comment was from Mardi and very hard to validate in the literature.)

@@

\begin{figure} % FIXME: Interesting these 2 regions probably have the highest price of grapes/tonne. They are also 2 extreme climates (Hunter = lots of grazing, season rainfall = of tractor passes. Tasmania = V.Cool weather = lots of tractor passes.)
 \resizebox{\textwidth}{!}{
 \includegraphics{profit.pdf}}
 \caption{Decision tree predicting Profit. Each node indicates the class predicted, and the proportion of elements agreeing with nodes partitioning, with the left direction indicating a yes to the nodes rule.}\label{fig:profit_tree}
\end{figure}

@@

% FIXME: Mardi again asked about whether yield was per hectare. This is areally interesting consideration - we do not look at predicting yield specifically in this though. perhaps we should be very wary about these analysis with this respect.

% FIXME: Moved here from results. Find a place for this lost puppy!
%
% It is reasonable that regions, being subjected to different rainfalls and temperatures, would require different amounts of water, and would have access to different water sources. The relation of area harvested and fuel (particularly petrol) is prominent with other predictors. Due to the wide variety of uses of petrol and diesel, it is likely that they are representative of 
% other activities within the vineyard, such as pruning and harvesting. FIXME: This is new infor tht doesnt have any context (e.g no discussion yet about what fuel may be used for)
% With predictors such as yield and area being highly interconnected as they likely operate as proxy variables to other factors, possibly other present variables.

Several physical parameters such as climate, geography and soil are predetermined by a vineyard's location; making it a widely considered key determinant of grape yield and quality \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,fragaMultivariateClusteringViticultural2017}. 
The association between yield and region is demonstrated by its position as fourth most occurring variable within the nodes of the XGBoosted ensemble which determined region (see Figure \ref{fig:region_sankey}). % FIXME: Clunky phrasing

The association with area and region is likely a connection to the change in land costs, with inland Australian areas (particularly of lower rainfall) being substantially cheaper to buy than coastal regions, allowing larger areas to be purchased \citep{willchancellorMeasuringAustralianBroadacre2019} % FIXME: Maybe but not sure this assumption holds. It may be an artefact of the members being corporate in larger holdings. The larger percentage of blocks in the riverland are small.

@@

Regions with lower land costs are also warmer \citep{willchancellorMeasuringAustralianBroadacre2019}, which is known to be beneficial in hastening the ripening process of winegrapes \citep{webbObservedTrendsWinegrape2011}. Warmer regions are also associated with lower quality grapes, caused largely due to this hastened ripening \citep{botting1996canopy}. In general if irrigated warmer regions have been associated with lower yields due to their generally lower rainfall, which can be mitigated through applying more water \citep{campsGrapeHarvestYield2012}. % FIXME: Rework this sentance
It is likely that the combination of larger vineyards with higher water use is a determining factor in classifying regions which favour larger production of lower quality grapes; reflected through the variables' importance of water use in the XGBoost ensemble. % FIXME: Need to link lower quality to profitability.
% FIXME: Warm inland regions are close to a major source of irrigation water which means that they have always taken advantage of this to grow higher crops. Which are also extremely important to our sector.)
% FIXME: May need to explain that growers are paid @ a $ value / tonne and that the $ value varies in region.
The practice of utilising larger quantities of water for inland Australian wine crops is partly reflected in the prior use of flood style irrigation to saturate soil \citep{bgcoombeGrapeBerryDevelopment2004}. % FIXME: More likely is that they have access to large water licences (Prev used for flood irrigation) That ythey now use on vineyards.
% FIXME: Examples of regions??
This classification can be contrasted with other warmer regions of higher rainfall that use the warmer climate to concentrate their grapes, increasing the flavour profile (and thus quality) \citep{goodwinijeriepRegulatedDeficitIrrigation1992,mgmccarthyEffectCropLoad1986}. This is possibly the connection between the presence of the Hunter Valley within the XGBoost ensemble that determined profit (see Figure \ref{fig:profit_sankey}). With this connection reflecting the restriction of possible strategies employable by winegrowers between different regions. % FIXME:  No this is because the hunter valley/tasmania get paid more / tonne.

@@

In part some winegrowing strategies are restricted simply through access to water resources, being reflected through the region classification tree (see Figure \ref{fig:region_tree}). Regions are likely to have varying access to different water sources, such as those along the River Murray being able to utilise river water for crops, unlike most coastal regions which may be drawing from surgace or underground water. Similarly, the connection between region and fuel use is likely an indicator of the level of infrastructure within the region. Where, the need to pressurise irrigation systems from river water or to generate power would require larger amounts of diesel and petrol. % FIXME: Yes but this requires some explanation

@@

Operational costs showed similar importance across fuel, water and tractor use. The dominating factor of area likely played a large part in determining how costly a tractor pass would be, or in defining the ratio of water applied to the amount of vines. The node frequency was high for area but much lower in general across the other variables, which could indicate the need to be more circumstantial in determining operational costs. Although it was attempted to capture the complexity between how variables interacted when determining operational costs (see Figure \ref{fig:operating_costs_sankey}), it is likely yet more complicated. An example of how interrelated operational costs can be, is 
the optimisation of tractor passes % FIXME: What does this mean? Multiple activities with a single pass?
being shown to reduce energy use in vineyards, decreasing running costs, as well as reducing soil compaction \citep{capelloEffectsTractorPasses2019}. 

@@

Decisions made on the ground have far-reaching effects and are difficult to completely capture. A higher number of tractor passes used as a preventative measure for occurrences such as disease, may incur higher operational costs but could be critical in preventing long term losses. With factors such as erosion and soil health being difficult to capture but also influenced by tractor use \citep{capelloEffectsTractorPasses2019,capelloPermanentCoverSoil2020}. Although, performing well in $R^2$, the ability to predict operational costs is limited by the variables incorporated. Reductions in fuel, water and tractor use are obvious methods to reduce operational costs but not necessarily achievable decisions. Without fully capturing more granular activities such as the specifics of what fuel was used for, it is hard to determine what decisions specifically influence the operational costs.

@@

Although less important in the XGBoost ensembles for profit, the variables: cover crops, and number of fungicide spraying and slashing passes are likely linked to broad environmental properties of regions (see Figure \ref{fig:region_sankey} and \ref{fig:profit_sankey}). Rainfall being related to vine fungal growth, disease and weed pressure. With cover crops being an effective and sustainable method to alleviate these issues \citep{delpuechAdaptingCoverCrop2018}. % FIXME: Re-structure this sentance.
It is difficult to extrapolate findings to these methods and the reason for their use due to the broad and varying definition of the regions. Utilising the Geographical Indicator regions defined by Wine Australia \citep{wineaustraliaWineAustraliaOpenData2021} is a limitation, as it is too broad to fully capture a vineyards location and its influence on more granular variables. The reasoning for using approaches such as cover crops can be widely varying. Where, a cover crop may be employed to help increase soil water retention, reduce erosion, increase biodiversity and reduce weeds \citep{capelloEffectsTractorPasses2019,capelloPermanentCoverSoil2020,delpuechAdaptingCoverCrop2018}. However, cover crops can introduce competition with grapevines and may reduce yield depending upon the plants used and the density of the cover crop \citep{goslingLongtermChangesSoil2005,monteiroInfluenceCoverCrop2007}. A more granular definition of region may help to better discern the differences in practices, and the reason for employing them. More sophisticated models, specifically those that utilise expert opinion, may also help to capture and address the decision making process. An example is the optimisation of fungicide sprays using Bayesian models that forecast disease risk \citep{luDiseaseRiskForecasting2020}.

@@

This study has provided valuable insights into the multifaceted dynamics governing operational costs, different yearly effects and vineyard regions highlighting the complex interrelatedness of variables within a vineyard. The paper underscores how factors such as water and fuel intersect to impact operational costs and How different seasonal events affect these operations and the significance of context-specific decision-making. While this investigation utilised a broad regional classification, the potential benefits of adopting a more nuanced approach and incorporating expert knowledge have been highlighted. By delving deeper into the complex interplay of variables, further advancements can be made in optimising vineyard management strategies for lowering operational costs and enhancing sustainability.

@@

 The classification tree and XGBoosted ensemble performed similarly for classifying year with 35.20\% (6.28\% standard deviation) and 51.81\% (42.20\% validation accuracy) respectively. Electricity and the type of irrigation were highly influential within the classification tree. Similarly, electricity was the most frequently occurring node in the XGBoost ensemble. Other variables such as slashing passes, and fungicide and herbicide spraying were more prevalent than in the classification tree. Weed and disease outbreaks are likely an influential factor when classifying different years, making the decisions to spray and slash unique factors that differ year to year. Climatic differences between years are likely tied to the influence of yield and water use.
 \par
 Over half of the interrelated importance of the predictor variables is dominated by area harvested, yield and slashing passes. Although all the predictor variables are highly connected, their relative importance is not as prominent as the three major variables. It is of particular note of the relative importance of slashing passes to area, fuel and yield; as these are not directly related activities. The connection between the number of slashing and spraying passes is that those who do a set number of spraying or slashing passes tended to do that many passes for all slashing and spraying activities.
